\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\renewcommand{\bibname}{Tài liệu tham khảo}
\begin{thebibliography}{99}
    \bibitem{whoiaq} World Health Organization, \textit{WHO guidelines for indoor air quality: selected pollutants}. WHO Regional Office for Europe, 2010.
    \bibitem{epaiaqstudent} United States Environmental Protection Agency, \textit{Indoor Air Quality and Student Performance}. EPA, 2003.
    \bibitem{pulimeno2020} M. Pulimeno, P. Piscitelli, S. Colazzo, A. Colao, and A. Miani, ``Indoor air quality at school and students' performance,'' \textit{Health Promotion Perspectives}, 2020.
    \bibitem{wargocki2020} P. Wargocki, J. A. Porras-Salazar, S. Contreras-Espinoza, and W. Bahnfleth, ``The relationships between classroom air quality and children's performance in school,'' \textit{Building and Environment}, 2020.
    \bibitem{canha2024} N. Canha, C. Correia, S. Mendez, C. A. Gamelas, and M. Felizardo, ``Monitoring Indoor Air Quality in Classrooms Using Low-Cost Sensors: Does the Perception of Teachers Match Reality?'' \textit{Atmosphere}, vol. 15, no. 12, 1450, 2024.
    \bibitem{renold2025} A. P. Renold, A. A. Abins, and J. Katiravan, ``IoT-Driven classroom air quality management with deep hierarchical cluster analysis,'' \textit{Scientific Reports}, 2025.
    \bibitem{merema2018} B. Merema, M. Delwati, M. Sourbron, and H. Breesch, ``Demand controlled ventilation in school and office buildings: Lessons learnt from case studies,'' \textit{Energy and Buildings}, 2018.
    \bibitem{epaiaqschools} United States Environmental Protection Agency, \textit{Reference Guide for Indoor Air Quality in Schools}. Truy cập ngày 2026-05-16 tại \url{https://www.epa.gov/iaq-schools/reference-guide-indoor-air-quality-schools}.
    \bibitem{alaiaqschools} American Lung Association, \textit{Indoor Air Quality in Schools Guide}. Truy cập ngày 2026-05-16 tại \url{https://www.lung.org/getmedia/14c45699-8055-4cdc-8695-7a57ae36058a/ALA-IAQ-School-V2.pdf}.
    \bibitem{whoaqg2021} World Health Organization, \textit{WHO Global Air Quality Guidelines}. Truy cập ngày 2026-05-16 tại \url{https://www.who.int/publications/i/item/9789240034228}.
    \bibitem{esp32soc} Espressif Systems, \textit{ESP32 Wi-Fi \& Bluetooth SoC}. Truy cập ngày 2026-05-16 tại \url{https://www.espressif.com/en/products/socs/esp32}.
    \bibitem{oasismqtt} OASIS, \textit{MQTT Version 5.0 OASIS Standard}. Truy cập ngày 2026-05-16 tại \url{https://docs.oasis-open.org/mqtt/mqtt/v5.0/mqtt-v5.0.html}.
    \bibitem{mqttorg} MQTT.org, \textit{MQTT: The Standard for IoT Messaging}. Truy cập ngày 2026-05-16 tại \url{https://mqtt.org/}.
    \bibitem{arduinoesp32} Espressif Systems, \textit{Arduino core for the ESP32}, tài liệu lập trình ESP32 với Arduino framework.
    \bibitem{modbus} Modbus Organization, \textit{MODBUS Application Protocol Specification}, tài liệu giao thức Modbus.
    \bibitem{pms7003} Plantower, \textit{PMS7003 Digital Universal Particle Concentration Sensor Datasheet}.
\end{thebibliography}
